Columnar VCF using Zarr

### 2024-03-12 paper.tex
Move some text to graveyard
Rough updates to show extrapolated genozip

\begin{figure*}
\includegraphics[width=6cm]{figures/subset-matrix-compute}
\caption{Compute performance on subsets of the matrix.
(A) Total CPU time required to run the afdist calculation for
a subset of 10 samples and 10000 variants from the middle of the matrix.
(B) Same for n/2 samples. Genozip did not run in this case for
$n > 10^4$ samples because it does not support a file to specify
sample IDs, and the command line was therefore too long for the shell
to execute.
(C) A simplified version of the source code used for these benchmarks.
\label{fig-subset-matrix-compute}}
\end{figure*}

>>>>

\begin{figure}
\includegraphics[width=6cm]{figures/subset-matrix-compute}
\caption{Compute performance on subsets of the matrix.
(A) Total CPU time required to run the afdist calculation for
a subset of 10 samples and 10000 variants from the middle of the matrix.
(B) Same for n/2 samples. Genozip did not run in this case for
$n > 10^4$ samples because it does not support a file to specify
sample IDs, and the command line was therefore too long for the shell
to execute. [TODO Note that in this case the bcftools pipeline requires
an additional step to compute AF etc.]
\label{fig-subset-matrix-compute}}
\end{figure}

\subsection{Non genotype data}

\begin{table}
\begin{tabular}{cc}
Some & data on Genomics England\\
\end{tabular}
\caption{Summary of vcf-zarr performance on the Genomics England 100,000
genomes VCF dataset.
\label{tab-genomics-england-data}}
\end{table}
